Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-01-03 lqg-strings.tex
Stuff

In this paper, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green_Schwarz_Witten_2012}

>>>>

In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green_Schwarz_Witten_2012}. To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
\begin{multline} \label{eqn:canonical-momentum}
	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \left( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \right) \eta _{\nu \mu} ,
\end{multline}
and then we proceed to turn the equal-time Poisson bracket relations
\begin{equation} \label{eqn:Poisson-brackets-1}
	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
\begin{equation} \label{eqn:Poisson-brackets-2}
	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
\end{equation}
into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
\begin{equation}
	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
